---
title: "ETC5521 Group Presentation"
subtitle: "How are the COVID-19 cases spreading in the Victorian community during 1st May to 30th September 2020?"
team: Beta
author:
  - Mohammed Faizan 
  - Prachi Jaiswal
  - Karan Garg
date: "`r Sys.Date()`"
output: 
  html_document:
    includes:
      before_body: header.html
bibliography: 
- packages.bib
biblio-style: authoryear-comp
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      messages = FALSE, 
                      cache = TRUE,
                     fig.path = "figures", 
                     fig.align ="center"
  )

library(tidyverse) 
library(lubridate)
library(plotly)
library(bookdown)
library(knitr)
library(ggthemes)
library(patchwork)
library(readr)
library(kableExtra)
library(tidytext)
library(dygraphs)
library(quantmod)
library(ggrepel)
library(tidyverse)
library(citation)
library(scales)
library(ggbeeswarm)
library(gt)
library(ggthemes)
library(leaflet)
library(DT)
library(sparkline)
library(formattable)
library(RColorBrewer)
library(sugarbag)
library(tsibble)
library(sugrrants)
library(naniar)
library(tidyr)
library(RefManageR)
library(sf)
library(glue)
library(unglue)
library(xts)
library(gghighlight)
library(networkD3)
library(ggplot2)
```

```{r writing_packages_bibliographies}
knitr::write_bib(c(.packages()), "packages.bib")
```

```{css, echo = FALSE}
.gray80 {
  color: #505050!important;
  font-weight: 300;
}
.bg-gray80 {
  background-color: #DCDCDC!important;
}
```


```{r, include=FALSE}
# lga_covid <- read_csv(here::here("data/VIC_COVID/COVID19 Data Viz LGA Data - lga.csv"))
# 
# postcode_covid <- read_csv(here::here("data/VIC_COVID/COVID19 Data Viz Postcode data - postcode.csv"))
# 
# cases_source <- read_csv(here::here("data/VIC_COVID/NCOV_COVID_Cases_by_Source_20211023.csv"))
# 
# lga_cases <- read_csv(here::here("data/VIC_COVID/NCOV_COVID_Cases_by_LGA_20211023.csv"))
covid_cases0 <- read_csv(here::here("data/VIC_COVID/NCOV_COVID_Cases_by_LGA_Source_20211023.csv")) %>% mutate(diagnosis_date=ymd(diagnosis_date)) %>% arrange(diagnosis_date)
covid_age <- read_csv(here::here("data/VIC_COVID/NCOV_COVID_Cases_by_Age_Group_20211023.csv"))%>% mutate(diagnosis_date=ymd(diagnosis_date)) %>% arrange(diagnosis_date) 
covid_cases <-  cbind(covid_cases0,covid_age %>% select(agegroup)) %>% 
  filter(diagnosis_date>="2020-05-01") %>% 
  filter(diagnosis_date<="2020-09-30")


covid_cases <- covid_cases %>% 
  mutate(
    Localgovernmentarea1=str_to_lower(
      str_trim(
        str_remove_all(Localgovernmentarea,"\\(.+\\)"))))


```


```{r}
data_path <- here::here("data/shape/boundaries/esrishape/whole_of_dataset/victoria/VMADMIN/")
postcode_boundaries <- read_sf(here::here(glue(data_path, "POSTCODE_POLYGON.shp"))) 
lga_boundaries <- read_sf(here::here(glue(data_path, "AD_LGA_AREA_POLYGON.shp")))%>% filter(STATE=="VIC") %>% 
  distinct(NAME,.keep_all = TRUE)

lga_boundaries <- lga_boundaries %>% 
  mutate(NAME1=str_to_lower(NAME)) %>% 
  distinct(NAME1,.keep_all = TRUE)
```

```{r}
postcodes <- as_tibble(postcode_boundaries) %>% select(-geometry)
lga <- as_tibble(lga_boundaries)%>% select(-geometry)
lga <- lga %>% 
  mutate(NAME1=str_to_lower(NAME)) %>% 
  distinct(NAME1,.keep_all = TRUE)
```



```{r}
date_case <-covid_cases %>% group_by(diagnosis_date) %>% summarise(n_cases = n()) %>% ungroup() %>% as_tsibble()
age <-covid_cases %>% group_by(diagnosis_date, agegroup) %>% summarise(n_cases = n())%>% ungroup()
acquired <-covid_cases %>% group_by(diagnosis_date, acquired) %>% summarise(n_cases = n())%>% ungroup()
pl <-covid_cases %>% group_by(diagnosis_date, Postcode, Localgovernmentarea1) %>% summarise(n_cases = n())%>% ungroup()

l_cases <- covid_cases %>% group_by(diagnosis_date, Localgovernmentarea1) %>% summarise(n_cases = n())%>% ungroup() %>% 
  arrange(Localgovernmentarea1,diagnosis_date) %>% 
  mutate(cum_cases = cumsum(n_cases))



l_month_cases <- covid_cases %>% mutate(month=month(diagnosis_date)) %>% 
  group_by(month, Localgovernmentarea1) %>% summarise(n_cases = n())%>% ungroup()%>% 
  arrange(Localgovernmentarea1,month) %>% 
  mutate(cum_cases = cumsum(n_cases))

pl_age <-covid_cases %>% group_by(diagnosis_date, Postcode, Localgovernmentarea1, agegroup) %>% summarise(n_cases = n())%>% ungroup()
```
```{r}
date_case %>% 
  select(n_cases) %>% 
  xts(order.by=date_case$diagnosis_date) %>% 
  dygraph( main = "Covid Cases across Months", xlab = NULL, ylab = NULL, periodicity = NULL,
  group = NULL, elementId = NULL, width = NULL, height = NULL)%>% 
  dyLegend(show = "always", hideOnMouseOut = FALSE)%>%
  dyAxis("y", label = "Temperature in Degree Celcius") %>%
  dyOptions(axisLineWidth = 1.5, fillGraph = FALSE, drawGrid = FALSE) %>% 
  dyRangeSelector()
```

```{r}
age %>% group_by(agegroup) %>% summarise(total=sum(n_cases)) %>% arrange(desc(total))
age <- age %>%  mutate(high=case_when(agegroup %in% c("20-29","30-39") ~ "high",
                             TRUE ~ "low"),
              low=case_when(agegroup %in% c("80-99","90+") ~ "low",
                             TRUE ~ "na"))
age %>% 
  ggplot(aes(x=diagnosis_date,y=n_cases)) +
  geom_line(color="red") +
  gghighlight(high == "high",
              use_direct_label = FALSE,
              calculate_per_facet = TRUE,
              keep_scales = TRUE) 
```





```{r}
variant_country <- readr::read_csv('https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/variants/covid-variants.csv') %>% filter(location=="Australia")
```

Now, we analyze the corona virus variants in Turkey. The first and basic visualisation to check the distribution of the variants is a bar plot. The variants are plotted on a bar chart and we find that the delta variant is the most common infection in Turkey. "The Delta variant is a variant of concern that WHO is tracking and monitoring around the world. It's a variant of concern because we know it has increased transmissibility. This has been demonstrated by several countries. And we know that where the Delta variant is identified, it really rapidly takes off and spreads between people more efficiently than even the Alpha variant that was first detected around December, January 2021. As of today, the Delta variant has been reported in 96 countries and we expect that the Delta variant will continue to spread." ~ Dr Maria Van Kerkhove


```{r}
variant_country <- variant_country %>% mutate(
  num_sequences=ifelse(is.na(num_sequences),0,num_sequences),
  perc_sequences=ifelse(is.na(perc_sequences),0,perc_sequences))%>% 
  mutate(year=year(date),
         month=month(date),
         day=day(date)) 
variant_summary <- variant_country %>% group_by(variant) %>% 
  summarise(variant_sum=sum(num_sequences))
variant_summary %>% filter(variant_sum>100) %>% ggplot(aes(x=reorder(variant,variant_sum),y=variant_sum)) + geom_col() +
  coord_flip() +
  theme_bw() +
  labs(y="Sum of Variants",title = "Variant Distribution",
         caption = "")  + 
        theme_classic()+
        labs(y = "Number of Cases",
         x = "Month",
         ) +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size = 11), 
        legend.position = "bottom")
 
  
```


Now, the first occurrence of the delta strain is identified and its relation with the increase in the number of cases will be discussed. The spread of the delta variant is super fast and it is proved by data in the plot below. The first occurence the delta variant in Turkey was in May 2021. The spread of it is so fast that, in August almost all of the cases are attributed to the delta variant. 


```{r}
variant_country_delta <- variant_country %>% filter(variant=="Delta") %>%
  mutate(month= month(date,label=TRUE,abbr = TRUE)) %>% 
  pivot_longer(cols=c(num_sequences,num_sequences_total),
               names_to = "sequence",
               values_to = "number") %>% 
  mutate(sequence=ifelse(sequence=="num_sequences","delta","total"))
variant_country_delta %>% ggplot(aes(x=month,y=number,fill=sequence)) + geom_col(position="dodge")+
        theme_classic()+
        labs(y = "Number of Cases",
         x = "Month",
         title = "Delta Variant Cases",
         caption = "Delta Variant Cases") +
  theme(axis.title.y = element_text(size = 11),
        axis.text.y = element_text(size = 11), 
        legend.position = "bottom")
```

Thus in all, I would say that the vaccination rate causes the infection rate to slow down. However, the neglected attitude of people and the hesitancy to take the vaccine has caused this pandemic to disturb normal life for longer times. The restrictions and other regulations have most definitely allowed us this time to face this pandemic in a stringer manner to avoid more deaths. Therefore, please get vaccinated and stay safe.


# 1

```{r}
sank <- covid_cases %>% 
  mutate(diagnosis_date = as.Date(diagnosis_date, format = "%d %b %Y"),
         day = day(diagnosis_date),
         month = month(diagnosis_date, label = TRUE), 
         year = year(diagnosis_date),
         month = as.factor(month)) %>%
  select(month, acquired) %>%
  group_by(month, acquired) %>%
  summarise(value = n()) %>%
  pivot_wider(names_from = acquired,
              values_from = value) %>%
  rename("Unknown"="Acquired in Australia, unknown source",
         "Contact"="Contact with a confirmed case",
         "Travel"="Travel overseas") %>%
  pivot_longer(cols = -month,
               names_to = "target",
               values_to = "value")
node <- data.frame(name=c(as.character(sank$month), 
        as.character(sank$target)) %>% unique())
my_color <- 'd3.scaleOrdinal() .domain(["Sep", "Oct", "Nov", "Covid", "War"]) .range([ "#5f0f40", "#fb8b24","#0f4c5c", "#9a031e", "#e36414"])'
sank$IDmonth <- match(sank$month, node$name)-1 
sank$IDtarget <- match(sank$target, node$name)-1
 
p <- sankeyNetwork(Links = sank, Nodes = node, Source = "IDmonth", 
               Target = "IDtarget", Value = "value", NodeID = "name", fontSize = 14, 
               nodeWidth = 20, nodePadding = 15, sinksRight = FALSE)
sankey <- htmlwidgets::prependContent(p, htmltools::tags$h4("Comparing Causes of Deaths in each Month"))
#sankey <- htmlwidgets::appendContent(sankey, htmltools::tags$p("Comparing Death Toll"))
sankey
```

```{r }
invthm <- theme_map() + 
  theme(
    panel.background = element_rect(fill = "black", colour = NA), 
    plot.background = element_rect(fill = "black", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.key = element_rect(fill = "transparent", colour = NA),
    text = element_text(colour = "white"),
    axis.text = element_blank()
  )
# function to allocate colours to regions
aus_colours <- function(sir_p50){
  value <- case_when(
    sir_p50 <  1000 ~ "#33809d",
    sir_p50 >= 1000 & sir_p50 < 3000 ~ "#FFFECC",
    sir_p50 >= 3000 & sir_p50 < 8000 ~ "#FFEDA0",
    sir_p50 >= 8000 & sir_p50 < 12000 ~ "#FED976",
    sir_p50 >= 12000 & sir_p50 < 16400 ~ "#FC4E2A",
    sir_p50 >= 16400 ~ "#800F26",
    TRUE ~ "#FFFFFF")
  return(value)
}

colors <- c("<1000","1000-3000","3000-8000","8000-12000","12000-16000",">16000")
l_month_cases <- l_month_cases %>% mutate(SIR = map_chr(cum_cases, aus_colours))


#cases suddenly rise in brimbank
l_month_cases %>% 
  filter(Localgovernmentarea1 %in% top10_lga) %>% 
  left_join(lga_boundaries, 
            by = c("Localgovernmentarea1"="NAME1")) %>%
  ggplot() +
  geom_sf(mapping = aes(geometry= geometry, fill=SIR)) +
  geom_sf_text(aes(geometry= geometry,label=Localgovernmentarea1, colour="white"), 
               check_overlap=TRUE)+
  scale_fill_brewer(labels=colors)+
  theme_void() +
  facet_wrap(~month)
```

```{r}

#brimbank cases
acq<- covid_cases %>% 
  filter(Localgovernmentarea1 == "brimbank") %>% 
  mutate(diagnosis_date = as.Date(diagnosis_date, format = "%d %b %Y"),
         day = day(diagnosis_date),
         month = month(diagnosis_date, label = TRUE), 
         year = year(diagnosis_date),
         month = as.factor(month)) %>%
  select(diagnosis_date, month, day, acquired) %>%
  group_by(diagnosis_date, month, day, acquired) %>%
  summarise(value = n()) %>%
  pivot_wider(names_from = acquired,
              values_from = value) %>%
  rename("Unknown"="Acquired in Australia, unknown source",
         "Contact"="Contact with a confirmed case",
         "Travel"="Travel overseas") %>%
  pivot_longer(cols = -c(diagnosis_date, day, month),
               names_to = "target",
               values_to = "value")

ggplot(acq, aes(x= day, y= value, color = target))+
  geom_line(size = 1.2)+
  theme_light()+
  facet_grid(~ month, scales='free_x')+
  scale_y_continuous(breaks = seq(0, 600, by = 100))+
  scale_color_brewer(name = "", palette = "Dark2")+
  labs(x= "Days",
       y= " Cases",
       title = "Cause of Increase in COVID-19 Infections",
       subtitle = "from May'20 to September'20 in Victoria, Melbourne")
```


```{r}
# Incorporate population data to make cartogram
# Population from https://www.planning.vic.gov.au/land-use-and-population-research/victoria-in-future/tab-pages/victoria-in-future-data-tables
# Data can be downloaded from https://github.com/numbats/eda/blob/master/data/VIF2019_Population_Service_Ages_LGA_2036.xlsx
pop <- read_xlsx(here::here("data/VIF2019_Population_Service_Ages_LGA_2036.xlsx"), sheet=3, skip=13, col_names = FALSE) %>%
  rename(NAME = `...4`, pop=`...22`) %>%
  filter(NAME != "Unincorporated Vic") %>% 
  mutate(NAME = str_replace(NAME, " \\(.+\\)", "")) %>%
  mutate(NAME = ifelse(NAME == "Colac-Otway", "colac otway", NAME)) %>%
  select(NAME, pop) %>% 
  mutate(NAME=str_to_lower(NAME))

l_month_cases1 <- l_month_cases %>%
  mutate(Localgovernmentarea1 = ifelse(Localgovernmentarea1 == "colac-otway", "colac otway", Localgovernmentarea1)) %>% 
  full_join(pop, by=c("Localgovernmentarea1"="NAME"))

# Compute additional statistics
l_month_cases1 <- l_month_cases1 %>%
  group_by(Localgovernmentarea1) %>%
  mutate(n_cases=ifelse(is.na(n_cases),0,n_cases),
         cum_cases=ifelse(is.na(cum_cases),0,cum_cases)) %>% 
  mutate(cases_per10k = max(n_cases/pop*10000, 0),
         lnew_cases = log10(n_cases - min(n_cases) + 1)) %>%
  ungroup()
  

library(ozmaps)
data("abs_lga")
vic_lga <- abs_lga %>%
  mutate(NAME = ifelse(NAME == "Latrobe (M) (Tas.)", "Latrobe", NAME)) %>%
  mutate(NAME = ifelse(NAME == "Kingston (DC) (SA)", "Kingston", NAME)) %>%
  mutate(NAME = ifelse(NAME == "Bayside (A)", "Bayside", NAME)) %>% 
  mutate(NAME = str_replace(NAME, " \\(.+\\)", "")) %>%
  mutate(NAME = ifelse(NAME == "Colac-Otway", "colac otway", NAME)) %>% 
  mutate(NAME1=str_to_lower(NAME)) %>% 
  distinct(NAME1,.keep_all = TRUE)

vic_lga <- st_transform(vic_lga, 3395)  %>% right_join(lga %>% select(NAME1)) %>% left_join(pop,by=c("NAME1"="NAME"))
vic_lga_carto <- st_cast(vic_lga, "MULTIPOLYGON")



vic_lga_covid <- vic_lga %>% left_join(l_month_cases1,
                                               by=c("NAME1"="Localgovernmentarea1",
                                                    "pop"="pop")) %>% 
  filter(!NAME1 %in% c("interstate","unknown")) %>% 
  filter(!is.na(pop)) %>% 
  mutate(n_cases=ifelse(is.na(n_cases),0,n_cases),
         cum_cases=ifelse(is.na(cum_cases),0,cum_cases))

# Make a contiguous cartogram
vic_lga_covid_carto <- cartogram_cont(vic_lga_covid, "pop")
# This st_cast() is necessary to get plotly to work
vic_lga_covid_carto <- st_cast(vic_lga_covid_carto, "MULTIPOLYGON") 

 ggplot(vic_lga_covid_carto) + 
  geom_sf(aes(fill=cum_cases), colour="white") + 
  scale_fill_distiller("Cases", palette = "YlOrRd",
                       direction=1) + 
  theme_map() +
  theme(legend.position="bottom") +
  facet_wrap(~month)

#map include for new cases 
 vic_lga_covid %>% 
   filter(!is.na(month)) %>% 
  ggplot() +
  geom_sf(mapping = aes(geometry= geometry, fill=n_cases)) +
  geom_sf_text(aes(geometry= geometry,label=NAME1, colour="white"), 
               check_overlap=TRUE)+
   transition_time(month) +
  #scale_fill_brewer(labels=colors)+
  theme_minimal() +
  facet_wrap(~month)
 
 
 
```



# 2

```{r }
date_case %>% 
  as_tibble() %>% 
  mutate(month=month(diagnosis_date,abbr = TRUE,label = TRUE)) %>% 
  group_by(month) %>%
  summarise("Total Cases" = round(sum(n_cases, na.rm = TRUE)),
            "Cases in a month" = spk_chr(n_cases, type ="line")) %>%
   arrange(month) %>% 
  rename(Month = month)%>%  
  datatable(rownames =TRUE, escape = FALSE, 
            caption = htmltools::tags$caption( style = 'caption-side: top; 
                                                text-align: center;  color:black; font-size:120% ;','COVID-19 Cases'),
            options=list(pageLength = 5)) %>%
  spk_add_deps() %>%
 formatStyle(
  "Total Cases",
  target = 'row',
  backgroundColor = styleInterval(c(0,1000000,Inf), c('black','white','green','red'))
) %>% 
  formatRound("Total Cases", digits = 0)
```

```{r}
#only for filtered data
postcodes1 <- covid_cases %>% select(Postcode) %>% 
  mutate(Postcode=as.character(Postcode)) %>% distinct() %>% 
  left_join(postcodes,
            by=c("Postcode"="POSTCODE")) %>% 
  rename("POSTCODE"="Postcode") %>% 
  left_join(postcode_boundaries)
```

```{r}

# lga <- lga %>% 
#   mutate(NAME1=str_to_lower(NAME)) %>% 
#   distinct(NAME1,.keep_all = TRUE)
# lga_boundaries <- lga_boundaries %>% 
#   mutate(NAME1=str_to_lower(NAME)) %>% 
#   distinct(NAME1,.keep_all = TRUE)

matchlganames <- tibble(l_cases=unique(l_cases$Localgovernmentarea1)) %>% 
  left_join(lga %>% select(NAME1),
                           by=c("l_cases"="NAME1"))


lga1 <- covid_cases %>% select(Localgovernmentarea1) %>% 
  distinct()  %>% 
  left_join(lga,
            by=c("Localgovernmentarea1"="NAME1")) %>% 
  rename("NAME1"="Localgovernmentarea1") %>% 
  left_join(lga_boundaries)
```

```{r}
top10_lga <- covid_cases %>% 
  group_by(Localgovernmentarea1) %>% 
  summarise(n_cases = n()) %>% 
  slice_max(n_cases,n = 5) %>% 
  pull(Localgovernmentarea1)
top10_postcode <- covid_cases %>% 
  group_by(Postcode) %>% 
  summarise(n_cases = n()) %>% 
  slice_max(n_cases,n = 10) %>% 
  pull(Postcode)
```





```{r }
data_path <- here::here("data/australian_census_data_2016/")
```


```{r datapath}
census_paths <- glue::glue(data_path, "/2016 Census GCP All Geographies for VIC/SA4/VIC/2016Census_G{number}{alpha}_VIC_SA4.csv", 
                         number = c("46","46","47","47","47","51","51","51","51","57","57", "52", "52", "52", "52", "58", "58"), alpha = c("A","B","A","B","C","A","B","C","D","A","B", "A","B","C","D", "A","B"))
```
```{r geopath}
data_path <- here::here("data/australian_census_data_2016/")
geopath <- glue::glue(data_path, "/2016_SA4_shape/SA4_2016_AUST.shp")
sa4_codes<- read_csv(census_paths[2]) %>% 
                mutate(SA4_CODE_2016 = as.character(SA4_CODE_2016)) %>% 
                select(SA4_CODE_2016)
sa4_geomap <- read_sf(geopath) %>%
  right_join(sa4_codes, by=c("SA4_CODE16" = "SA4_CODE_2016"))
```



```{r g51read}
g51 <- map_dfr(census_paths[6:8], ~{
  df <- read_csv(.x) %>%
      select(-starts_with("P"), -contains("Tot")) %>%
            mutate(SA4_CODE_2016 = as.character(SA4_CODE_2016)) %>% 
  pivot_longer(cols = -c(SA4_CODE_2016),
                  names_to = "category",
                  values_to = "count") %>%
  unglue_unnest(category, 
                    c("{sex=[MF]}_{industry=(Ag_For_Fshg|Mining|Manufact|El_Gas_Wt_Waste|Constru|WhlesaleTde|RetTde|Accom_food|Trans_post_wrehsg|Info_media_teleco|Fin_Insur|RtnHir_REst|Pro_scien_tec|Admin_supp|Public_admin_sfty|Educ_trng|HlthCare_SocAs|Art_recn|Oth_scs|ID_NS)}_{age_min=\\d+}_{age_max=\\d+}",
                      "{sex=[MF]}_{industry=(Ag_For_Fshg|Mining|Manufact|El_Gas_Wt_Waste|Constru|WhlesaleTde|RetTde|Accom_food|Trans_post_wrehsg|Info_media_teleco|Fin_Insur|RtnHir_REst|Pro_scien_tec|Admin_supp|Public_admin_sfty|Educ_trng|HlthCare_SocAs|Art_recn|Oth_scs|ID_NS)}_{age_min=\\d+}ov"
                     ),
                remove = FALSE)
})
```
```{r g51rename}
g51 <- g51 %>% 
  mutate(industry =case_when(
                            str_detect(industry, "Ag_For_Fshg") ~ "Agriculture_forestry_and_fishing",
                            str_detect(industry, "Manufact") ~ "Manufacturing",
                            str_detect(industry, "El_Gas_Wt_Waste") ~ "Electricity_gas_water_and_waste_service",
                            str_detect(industry, "Constru") ~ "Construction",
                            str_detect(industry, "Ag_Envir_Rltd_Sts") ~ "Agriculture_Environment",
                            str_detect(industry, "WhlesaleTde") ~ "Wholesale_trade",
                            str_detect(industry, "RetTde") ~ "Retail_trade",
                            str_detect(industry, "Accom_food") ~ "Accommodation_and_food_services",
                            str_detect(industry, "Trans_post_wrehsg") ~ "Transport_postal_and_warehousing",
                            str_detect(industry, "Info_media_teleco") ~ "Information_media_and_telecommunications",
                            str_detect(industry, "Fin_Insur") ~ "Financial_and_insurance_services",
                            str_detect(industry, "RtnHir_REst") ~ "Rental_hiring_and_real_estate_services",
                            str_detect(industry, "Pro_scien_tec") ~ "Professional_scientific_and_technical_services",
                            str_detect(industry, "Admin_supp") ~ "Administrative_and_support_services",
                            str_detect(industry, "Public_admin_sfty") ~ "Public_administration_and_safety",
                            str_detect(industry, "Educ_trng") ~ "Education_and_training",
                            str_detect(industry, "HlthCare_SocAs") ~ "Health_care_and_social_assistance",
                            str_detect(industry, "Art_recn") ~ "Arts_and_recreation_services",
                            str_detect(industry, "Oth_scs") ~ "Other_services",
                            str_detect(industry, "ID_NS") ~ "Not Stated",
                            TRUE ~ industry))  %>%
  select(-category) %>%
  rename(count_industry = count)
```
```{r}
vicpopulation <- g51 %>%
  group_by(SA4_CODE_2016) %>%
  summarise(population = sum(count_industry)) %>%
  ungroup()
population <- vicpopulation %>%
  summarise(population=sum(population))
vicpopulation <- g51 %>%
  group_by(SA4_CODE_2016, sex) %>%
  summarise(population = sum(count_industry)) %>%
  ungroup(sex) %>%
  pivot_wider(names_from = sex,
              values_from = population) %>%
  rename(malepopulation = M,
         femalepopulation = `F`) %>%
  full_join(vicpopulation)
```
```{r}
vicpopulation %>% 
  full_join(sa4_geomap, 
            by = c("SA4_CODE_2016"="SA4_CODE")) %>%
  ggplot() +
  geom_sf(mapping = aes(geometry= geometry, fill=population)) +
  geom_sf_text(aes(geometry= geometry,label=SA4_CODE_2016, colour="white"), 
               check_overlap=TRUE)+
  theme_void() 
```

# 3
```{r,include=FALSE}
top_lga1 <- covid_cases %>% 
  group_by(Localgovernmentarea) %>% 
  summarise(n_cases  = n()) %>% 
  ungroup() %>% 
  slice_max(n_cases,n=10) %>% 
  mutate(Localgovernmentarea = str_sub(Localgovernmentarea,0,str_length(Localgovernmentarea) -3),
         Localgovernmentarea = trimws(Localgovernmentarea)) %>% 
  select(Localgovernmentarea)
top_lga <- top_lga1$Localgovernmentarea
```
```{r linelga,warning=FALSE,message=FALSE,echo=FALSE,fig.width=6, fig.height=2,out.width="100%"}
graphlga <- covid_cases %>% 
  separate(diagnosis_date,into = c("Year","Month","Day"),sep = "-") %>% 
  mutate(Localgovernmentarea = str_sub(Localgovernmentarea,0,str_length(Localgovernmentarea) -3),
         Localgovernmentarea = trimws(Localgovernmentarea)) %>% 
  filter(Localgovernmentarea %in% top_lga) %>% 
  group_by(Month,Localgovernmentarea) %>% 
  summarise(n_cases = n()) %>% 
  ungroup() %>% 
  mutate(Month = as.numeric(Month)) %>% 
  mutate(tooltip = glue::glue(
           "Month: {Month}
            Covid Cases: {n_cases}
            LGA: {Localgovernmentarea}
           "
         )) %>% 
  ggplot(aes(Month,
             n_cases,
             color = Localgovernmentarea)) +
  geom_line() +
  geom_point(aes(text = tooltip)) +
  scale_x_continuous() +
  labs(x = "Month",
       y = "No. of Cases",
       title = "Trend of Top 10 LGA with maximum Covid Cases",
       color = NULL) +
  theme_bw()
ggplotly(graphlga,
         tooltip = "text") 

  
```

```{r,include=FALSE}
library(ggraph)
library(tidygraph)
clean_selected <- covid_cases %>% 
  separate(diagnosis_date,into = c("Year","Month","Date"),sep = "-") %>% 
  group_by(Month,acquired,Localgovernmentarea) %>% 
  summarise(n_cases = n()) %>% 
  ungroup() %>%
  select(acquired,Localgovernmentarea,n_cases) %>% 
  mutate(acquired = as.factor(acquired),
         Localgovernmentarea = as.factor(Localgovernmentarea),
         aclg = paste0(acquired,Localgovernmentarea)) 
graph_dt <- clean_selected %>% 
  group_by(aclg) %>% 
  summarise(total_cases = sum(n_cases)) %>% 
  left_join(clean_selected, by = "aclg") %>% 
  rename(from = acquired, to = Localgovernmentarea) %>% 
  as_tbl_graph()
acquired1 <- covid_cases %>% select(acquired) %>% unique()  
acquired <- acquired1$acquired 
lga1 <- covid_cases %>% select(Localgovernmentarea) %>% unique()  
lga <- lga1$Localgovernmentarea 
structure <- c(acquired,lga)
```



```{r}
set.seed(1234)
ggraph(graph_dt, "lgl") +
  geom_edge_link2(color = "grey90") +
  geom_node_point(data = ~.x %>% filter(name %in% structure)) + 
  geom_node_label(data = ~.x %>% filter(name %in% structure),
                  aes(label = name), repel = TRUE, 
                  label.size = NA,  fill = "orange") +
  geom_node_label(data = ~.x %>% filter(!name %in% structure),
                  aes(label = name), size = 2, 
                  label.size = 0.1,  fill = "lightblue2") +
  scale_edge_color_brewer(palette = "Dark2") + 
  theme_void()
```















```{r}
# Incorporate population data to make cartogram
# Population from https://www.planning.vic.gov.au/land-use-and-population-research/victoria-in-future/tab-pages/victoria-in-future-data-tables
# Data can be downloaded from https://github.com/numbats/eda/blob/master/data/VIF2019_Population_Service_Ages_LGA_2036.xlsx
pop <- read_xlsx(here::here("data/VIF2019_Population_Service_Ages_LGA_2036.xlsx"), sheet=3, skip=13, col_names = FALSE) %>%
  rename(NAME = `...4`, pop=`...22`) %>%
  filter(NAME != "Unincorporated Vic") %>% 
  mutate(NAME = str_replace(NAME, " \\(.+\\)", "")) %>%
  mutate(NAME = ifelse(NAME == "Colac-Otway", "colac otway", NAME)) %>%
  select(NAME, pop) %>% 
  mutate(NAME=str_to_lower(NAME))

data("abs_lga")
vic_lga <- abs_lga %>%
  mutate(NAME = ifelse(NAME == "Latrobe (M) (Tas.)", "Latrobe", NAME)) %>%
  mutate(NAME = ifelse(NAME == "Kingston (DC) (SA)", "Kingston", NAME)) %>%
  mutate(NAME = ifelse(NAME == "Bayside (A)", "Bayside", NAME)) %>% 
  mutate(NAME = str_replace(NAME, " \\(.+\\)", "")) %>%
  mutate(NAME = ifelse(NAME == "Colac-Otway", "colac otway", NAME)) %>% 
  mutate(NAME1=str_to_lower(NAME)) %>% 
  distinct(NAME1,.keep_all = TRUE)

vic_lga <- st_transform(vic_lga, 3395) 
# %>% right_join(lga %>% select(NAME1)) %>% left_join(pop,by=c("NAME1"="NAME"))

vic_lga_covid <- vic_lga %>%
  left_join(l_month_cases, by=c("NAME1"="Localgovernmentarea1")) %>%
  filter(!is.na(n_cases))

ggplot(vic_lga_covid) + 
  geom_sf(aes(fill = n_cases, label=NAME), colour="white") + 
  scale_fill_distiller("Cases", palette = "YlOrRd",
                       direction=1) + 
  facet_wrap(~month) +
  theme_map() +
  theme(legend.position="bottom")



l_month_cases1 <- l_month_cases %>%
  mutate(Localgovernmentarea1 = ifelse(Localgovernmentarea1 == "colac-otway", "colac otway", Localgovernmentarea1)) %>% 
  full_join(pop, by=c("Localgovernmentarea1"="NAME"))

vic_lga_covid <- vic_lga %>%
  left_join(l_month_cases1, by=c("NAME1"="Localgovernmentarea1")) %>%
  filter(!is.na(n_cases))




  

 
# Make a contiguous cartogram just with one and use with all
vic_lga_covid_carto <- cartogram_cont(vic_lga_covid %>% filter(month==8), "pop")
# This st_cast() is necessary to get plotly to work
vic_lga_covid_carto <- st_cast(vic_lga_covid_carto, "MULTIPOLYGON") 

 # ggplot(vic_lga_covid_carto) + 
 #  geom_sf(aes(fill=cum_cases), colour="white") + 
 #  scale_fill_distiller("Cases", palette = "YlOrRd",
 #                       direction=1) + 
 #  theme_map() +
 #  theme(legend.position="bottom") +
 #  facet_wrap(~month)
 
```


```{r}
covid_week <- covid_cases %>% 
  mutate(week = week(diagnosis_date)) %>%
  group_by(Localgovernmentarea1, week) %>%
  summarise(wk_cases = n())%>%
  ungroup() %>%
  left_join(pop, , by=c("Localgovernmentarea1"="NAME")) %>% 
  group_by(Localgovernmentarea1, week) %>%
  mutate(wk_cases_per10k = max(wk_cases/pop*10000, 0)) %>%
  ungroup()

vic_lga_covid_week <- vic_lga %>%
  left_join(covid_week,by=c("NAME1"="Localgovernmentarea1")) %>%
  filter(!is.na(wk_cases))


# Draw the faceted map
# ggplot(vic_lga_covid_week) + 
#   geom_sf(aes(fill = wk_cases), colour="white") + 
#   scale_fill_distiller("Cases", palette = "YlOrRd",
#                        direction=1) + 
#   facet_wrap(~week, ncol=5) +
#   theme_map() +
#   theme(legend.position="bottom")

# Join to the cartogram
vic_lga_covid_week_carto <-
  vic_lga_covid_carto %>%
  left_join(covid_week,by=c("NAME1"="Localgovernmentarea1","pop"="pop")) 

# Make the facetted cartogram
# ggplot(vic_lga_covid_week_carto) + 
#   geom_sf(aes(fill = wk_cases_per10k), colour="white") + 
#   scale_fill_distiller("Cases", palette = "YlOrRd",
#                        direction=1) + 
#   facet_wrap(~week, ncol=4) +
#   theme_map() +
#   theme(legend.position="bottom")
```

```{r}
vic_lga_covid1 <- vic_lga_covid %>% as_tibble() %>% distinct(NAME1) %>% 
  left_join(vic_lga) %>% st_as_sf()

# Spatial coordinates need to be in long/lat
vlc_latlong <- st_transform(vic_lga_covid1, crs = "+proj=longlat +datum=WGS84")

# Placement of hexmaps depends on position relative to
# Melbourne central
data(capital_cities)
vic_lga_hexmap <- create_hexmap(
  shp = vlc_latlong,
  sf_id = "NAME1",
  focal_points = capital_cities, verbose = TRUE)
# This shows the centroids of the hexagons
ggplot(vic_lga_hexmap, aes(x=hex_long, y=hex_lat)) +
  geom_point()
```

```{r}


# Hexagons are made with the `fortify_hexagon` function
vic_lga_covid_week_hexmap <- vic_lga_hexmap %>%
  fortify_hexagon(sf_id = "NAME1", hex_size = 0.1869) %>%
  left_join(covid_week, by=c("NAME1"="Localgovernmentarea1"))

vic_lga_covid_week_hexmap <- vic_lga_covid_week_hexmap %>% 
  mutate(tooltip=glue::glue_data(vic_lga_covid_week_hexmap,
                                 "LGA: {NAME1}",
                                 "\nwk_cases_per10k: {round(wk_cases_per10k)}"))
map1 <- ggplot() +
  geom_sf(data=vlc_latlong, 
          fill = "grey90", colour = "white", size=0.1) +
  geom_polygon(data=vic_lga_covid_week_hexmap %>% filter(week %in% c(27:32)), 
               aes(x=long, y=lat, group=hex_id, text=tooltip,
                   fill = wk_cases_per10k, 
                   colour = wk_cases_per10k), size=0.2) +
  scale_fill_distiller("Cases", palette = "YlOrRd",
                       direction=1) +
  scale_colour_distiller("Cases", palette = "YlOrRd",
                       direction=1) +
  facet_wrap(~week, ncol=3) +
  theme_map() +
  theme(legend.position="bottom")

map1 <- ggplotly(
      map1,
      tooltip = "text"
    )
map1


ggplot(vic_lga_covid_week_carto) + 
  geom_sf(aes(fill = wk_cases_per10k), colour="white") + 
  scale_fill_distiller("Cases", palette = "YlOrRd",
                       direction=1) + 
  facet_wrap(~week, ncol=4) +
  theme_map() +
  theme(legend.position="bottom")

```


